Wikipedia Text Mining and Surprisal Analysis

### 2019-05-30 surprisal/wiki_surprisal.Rmd
childes unigrams
reorganized surprisal folder more
tiny change to filepath in wiki_surprisal

```{r word order}
wkpd <- read.csv(here("relative_unigrams.csv"))
LANGUAGES <- wkpd$Language

@@

feature_names <- read_feather(here("feature_names.feather"))

>>>>

```{r make dendrogram}
wiki <- read.csv(here("Data/relative_unigrams.csv")) %>%
  select(-X) %>% 
  column_to_rownames("Language")

wiki %>% 
  dist() %>% 
  hclust() %>% 
  plot(hang = -1, 
       main = "Dendrogram of slope embeddings")

```

```{r word order}
wkpd <- read.csv(here("Data/relative_unigrams.csv"))
LANGUAGES <- wkpd$Language

@@

feature_names <- read_feather(here("Wikipedia/feature_names.feather"))
